Toxic code snippets on Stack Overflow

### 2017-10-22 cloverflow-tse/cloverflow.tex
Checked the paper, corrected issues and added a few FIXMEs.

\lstset{language=Java,
	tabsize=2,
	basicstyle=\ttfamily\footnotesize,
	moredelim=[is][\dotuline]{@}{@},
	mathescape=true
}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples in questions and answers. % They
Due to an absence of a checking mechanism after the code has been copied to
Stack Overflow, they can become toxic code snippets, i.e.~ they suffer from
being outdated or violating the original software license. We present a study
incorporating several state-of-the-art tools and techniques to automatically
extract and filter detected online clone pairs between 72,365 Java code snippets
on Stack Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
Our investigation of the online clone pairs revealed strong evidence that 154
clones have been copied from a Qualitas project to Stack Overflow.  We found 101
of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
we found 214 code snippets on Stack Overflow that violate the license of their
original software. We surveyed 201 high-reputation Stack Overflow answerers
(33\% response rate) and found that 69 of them have never been notified of
outdated code in the answers and 26 of them rarely or never fix the outdated
code. Only 3 answerers explicitly include software license in their answers and
138 answerers never check for licensing conflicts between their copied code
snippets and Stack Overflow's CC BY-SA 3.0.
\end{abstract}

@@

%The popularity of the Internet encourages tremendous amount of source code being shared online. 
Stack Overflow is a popular online programming community with 7.6
million users, 14 million questions, and 23 million answers\footnote{Data as of 21
	August 2017 from~\url{https://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
to programming problems. The website has found to be useful for
software
development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also
valuable for educational purposes~\cite{Nasehi2012}. On Stack
Overflow, each conversation contains a question and a list of
answers. The answers frequently contain at least one code snippet as
a solution to the question asked. We found that the code snippets are
usually not authored directly on the Stack Overflow website but copied
from another location. A snippet in an answer could be copied and modified
from a code snippet in the question, copied from the answerer's own
code or from other locations including open source software (OSS)
systems. The process of posting and answering questions on Stack
Overflow that involves the reuse of source code can be considered
code cloning.

Code cloning is an activity of reusing source code by copying and
pasting. It normally occurs in software development and account from
7\% to 23\% of source code in typical software
systems~\cite{Bellon2007}. The benefits and drawbacks of clones are
still controversial. Several authors state that clones lead to bug
propagations and software maintenance issues~\cite{Kamiya2002}, while
some others suggest that clones are not harmful and can even be
beneficial~\cite{Saini2016,Kapser2006}.

@@

Toxic code snippets mean code snippets that are harmful for reuse and, in
several cases, are caused by online code cloning. Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1) outdated or (2) violating their original software license. Outdated code
can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license , e.g.~GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting license, legal issues may occur.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2014-11-21) */
public int compare(byte[] b1,int s1,int l1, ...) {    public int compare(byte[] b1,int s1,int l1, ...) {
  try {                                                 try {
    buffer.reset(b1,s1,l1); /* parse key1 */              buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                              key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */              buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                              key2.readFields(buffer);
  } catch (IOException e) {                               $$@buffer.reset(null,0,0); /* clean up reference */@
    throw new RuntimeException(e);                      } catch (IOException e) {
  }                                                       throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */         }
}                                                       return compare(key1, key2); /* compare them */
                                                      }
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{WritableComparator.java}}. The one from the
		Stack Overflow post 22315734 (left) is outdated when compared to
		its latest version in the \textsf{hadoop} code base
		(right). Its Apache v.2.0 license is also missing.~\FIXME{@Jens Could you please make the underline clearer?}}
	\label{fig:before-after}
\end{figure*}

We would like to motivate the readers by giving two examples of toxic
cod snippets.
The first example is outdated and license-violating online code clones in an
answer to a Stack Overflow question regarding how to implement
{\small{\texttt{RawComparator}}} in
\textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
\Cref{fig:before-after} shows---on the left---a code snippet embedded as a part
of the accepted answer. The snippet shows how \textsf{hadoop} implements the
{\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}}
class. The code snippet on the right shows another version of the same method,
but at this time extracted from the latest version (as of October 3, 2017) of
\textsf{hadoop}. We can see that they both are highly similar except a line
containing {\small{\verb|buffer.reset(null,0,0);|}} which was added on November
21, 2014. The added line is intended for cleaning up the reference in the
{\small{\verb|buffer|}} variable and avoid excess heap usage
(issue no.~HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
While this change has already been introduced into the
{\small{\texttt{compare}}} method for several years, the code example in Stack
Overflow post is still unchanged. 
%This example shows that inconsistencies
%between online code clones and their originals can lead users of Stack Overflow
%to reuse outdated code. 
In addition, the original code snippet of
{\small\texttt{WritableComparator}} class in Hadoop is distributed with Apache license
version 2.0 while its cloned instance on Stack Overflow contains only the
{\small{\texttt{compare}}} method and ignores its license statement on top of the
file. There are two potential issues for this. First, the code snippet may appear to be 
under Stack Overflow's CC BY-SA 3.0 instead of its original Apache
license. Second, if the code snippet is copied and incorporated into another
software project with a conflicting license, a legal issue may arise.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 801987 */             /* StringUtils.java (2013-02-05) */
public static String humanReadableInt(long number) {    public static String humanReadableInt(long number) {
  long absNumber = Math.abs(number);                      return TraditionalBinaryPrefix.long2String(number,"",1);
  double result = number;                               }
  String suffix = "";
  if (absNumber < 1024) {
  } else if (absNumber < 1024 * 1024) {
    result = number / 1024.0;
    suffix = "k";
  } else if (absNumber < 1024 * 1024 * 1024) {
    result = number / (1024.0 * 1024);
    suffix = "m";
  } else {
    result = number / (1024.0 * 1024 * 1024);
    suffix = "g";
  }
  return oneDecimal.format(result) + suffix;
}
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{StringUtils.java}}. The one from the
		Stack Overflow post 801987 (left) is outdated when compared to
		its latest version in the \textsf{hadoop} code base
		(right). The toxic code snippet is outdated code, has race conditions, and does not contain its
		original Apache v.2.0 license.}
	\label{fig:before-after_2}
\end{figure*}

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{hadoop}. We can see that
they are totally different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
The absence of Apache v.2.0 license also occurs after the snippet is posted on 
Stack Overflow.

The two toxic code snippet in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times as
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet in approximately every 5
days compared to almost every day for the second one. A quick web search shows
that the defective {\small{\texttt{humanReadableInt}}} method in the second
example already appears in approximately 500 projects on GitHub. Considering the
popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippets on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,302 online clones, at least 330 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 154 of them, we found evidence that they have been copied
	from a specific open source project and that 101 of them are outdated. %
	% and questionable for being reused.

	\item \textbf{Awareness of Stack Overflow answerers to toxic code snippets:} We
	performed an online survey and collected answers from 201 highly-ranked Stack
	Overflow users. We found that they cloned code snippets from open source
	projects to Stack Overflow answers. While Stack Overflow answerers are aware of
	their outdated code snippets, 19\% of the participants rarely
	or never fix the code. 99\% of the answerers never include software
	license in their snippets and 69\% never check for licensing conflicts between the
	cloned code snippets and Stack Overflow's CC BY-SA 3.0.

@@

\textbf{Stack Overflow:} We extracted Java code snippets from a snapshot of a
Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. % The archived dump has a size of 9 gigabytes.
The data dump is in XML, and it contains information of posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode}
methods, which are not interesting for the study. Each snippet was extracted
from the dump and saved to a file. Moreover, we filtered out irrelevant code
snippets that were part of the accepted answers but were not written in Java by
using regular expressions and manual checking. ~\FIXME{@Jens, should I mention I
	use PMD CPD to help filtering SO code snippets here? Will it be too confusing?}.
Finally we obtained 72,365 Java code snippets containing 1,840,581
lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
source code. The median size of the snippet is 17 lines.

@@

\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	%\small
	\begin{tabular}{lrrr}
		\toprule
		Dataset & No. of files & SLOC & Median \\
		\midrule
		Stack Overflow & 72,365 & 1,840,581 & 17 \\ 
		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
		\bottomrule
	\end{tabular} 
\end{table}

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. %\textbf{Clone Detection and Configuration: }
There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to the nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution due to lexical errors. iClones
could complete its execution but skipped 367 snippets due to malformed blocks in
Stack Overflow data sets. CCFinder reported 8 errors while processing the two data set. 
Although Simian, SourcererCC, and DECKARD
could successfully report clones, we decided to choose only Simian and
SourcererCC due to their fast detection speed.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2)~\cite{Bellon2007}. \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}.

@@

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. All variable renaming are disabled to decrease the number of
false positives since we aim for finding clones that are copied from open source
projects with minimal modifications. The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statments (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\ We follow Bellon's original definitions of ok-match~\cite{Bellon2007}, which are based on how much two clone
fragments \textit{CF} are contained in each other:

%\squeezeup
%\begin{displaymath}
%overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
%\end{displaymath}
% \squeezeup
\begin{displaymath}
contained(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
\end{displaymath}
\noindent%
A clone pair \textit{CP} is formed by two clone fragments
\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} =
(\textit{CF$_1$}, \textit{CF$_2$})
%, and the \textit{good-value} and
and the \textit{ok-value} of two clone pairs are defined as

@@

Using the ok-match criterion with a predefined threshold \textit{t} of 0.7
similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC into a single set of 2,302 online
clone pairs. There are 97 common clone pairs between the two clone sets 
as depicted in~\Cref{fig:clonemerging}.

@@

		UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
		\midrule
		BP & Boiler-plate or IDE auto-generated \\

@@

\textbf{To answer RQ1, we found more than half of Qualitas projects to share
	similar code with Stack Overflow code snippets. In the manually confirmed 
	data set of 2,302 clone pairs, we found 2,076 pairs as true positives which 
	account for 59 Qualitas projects and
	443 Stack Overflow code snippets.}

>>>>

\lstset{language=Java,
	tabsize=2,
	basicstyle=\ttfamily\footnotesize,
	mathescape=true
}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples in questions and answers. % They
Due to an absence of a checking mechanism after the code has been copied to
Stack Overflow, they can become toxic code snippets, i.e.~ they suffer from
being outdated or violating the original software license. We present a study
incorporating several state-of-the-art tools and techniques to automatically
extract and filter detected online clone pairs between 72,365 Java code snippets
on Stack Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
Our investigation of the online clone pairs revealed strong evidence that 154
clones have been copied from a Qualitas project to Stack Overflow.  We found 101
of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
we found 214 code snippets on Stack Overflow that violate the license of their
original software. We surveyed 201 high-reputation Stack Overflow answerers
(33\% response rate) and found that 69 of them (FIXME\%) have never been notified of
outdated code in the answers and 26 of them (FIXME\%) rarely or never fix the outdated
code. Only 3 answerers explicitly include software license in their answers and
138 answerers (FIXME\%) never check for licensing conflicts between their copied code
snippets and Stack Overflow's CC BY-SA 3.0.
\end{abstract}

@@

%The popularity of the Internet encourages tremendous amount of source code being shared online. 
Stack Overflow is a popular online programming community with 7.6
million users, 14 million questions, and 23 million answers\footnote{Data as of 21
	August 2017 from~\url{https://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
to programming problems. The website has found to be useful for
software
development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also
valuable for educational purposes~\cite{Nasehi2012}. On Stack
Overflow, each conversation contains a question and a list of
answers. The answers frequently contain at least one code snippet as
a solution to the question asked. We found that the code snippets are
usually not authored directly on the Stack Overflow website but copied
from another location. A snippet in an answer could be copied and modified
from a code snippet in the question, copied from the answerer's own
code or from other locations including open source software (OSS)
systems.

The process of posting and answering questions on Stack
Overflow that involves the reuse (copying) of source code can be considered
code cloning.
Code cloning is an activity of reusing source code by copying and
pasting. It normally occurs in software development and account from
7\% to 23\% of source code in typical software
systems~\cite{Bellon2007}. The benefits and drawbacks of clones are
still controversial. Several authors state that clones lead to bug
propagations and software maintenance issues~\cite{Kamiya2002}, while
some others suggest that clones are not harmful and can even be
beneficial~\cite{Saini2016,Kapser2006}.

@@

Toxic code snippets mean code snippets that are harmful for reuse and, in
several cases, are caused by online code cloning. Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1) outdated or (2) violating their original software
license. Outdated code snippets
can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license , e.g.~GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

\begin{figure*}
  \fboxsep0pt
	\begin{lstlisting}[escapechar=&]
/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2014-11-21) */
public int compare(byte[] b1,int s1,int l1, ...) {    public int compare(byte[] b1,int s1,int l1, ...) {
  try {                                                 try {
    buffer.reset(b1,s1,l1); /* parse key1 */              buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                              key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */              buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                              key2.readFields(buffer);
  } catch (IOException e) {                               &\framebox{buffer.reset(null,0,0); \textit{/* clean up reference */}}&
    throw new RuntimeException(e);                      } catch (IOException e) {
  }                                                       throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */         }
}                                                       return compare(key1, key2); /* compare them */
                                                      }
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{WritableComparator.java}}. The one from the
		Stack Overflow post 22315734 (left) is outdated when compared to
		its latest version in the \textsf{Hadoop} code base
		(right). Its Apache v.2.0 license is also missing.}
	\label{fig:before-after}
\end{figure*}

We would like to motivate the readers by giving two examples of toxic
cod snippets.
The first example is outdated and license-violating online code clones in an
answer to a Stack Overflow question regarding how to implement
{\small{\texttt{RawComparator}}} in
\textsf{Hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
\Cref{fig:before-after} shows---on the left---a code snippet embedded as a part
of the accepted answer. The snippet shows how \textsf{Hadoop} implements the
{\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}}
class. The code snippet on the right shows another version of the same method,
but at this time extracted from the latest version (as of October 3, 2017) of
\textsf{Hadoop}. We can see that they both are highly similar except a line
containing {\small{\verb|buffer.reset(null,0,0);|}} which was added on November
21, 2014. The added line is intended for cleaning up the reference in the
{\small{\verb|buffer|}} variable and avoid excess heap usage
(issue no.~HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
While this change has already been introduced into the
{\small{\texttt{compare}}} method several years ago, the code example in Stack
Overflow post is still unchanged. 
%This example shows that inconsistencies
%between online code clones and their originals can lead users of Stack Overflow
%to reuse outdated code. 
In addition, the original code snippet of
{\small\texttt{WritableComparator}} class in Hadoop is distributed with Apache license
version 2.0 while its cloned instance on Stack Overflow contains only the
{\small{\texttt{compare}}} method and ignores its license statement on top of the
file. There are two potential issues for this. First, the code snippet may appear to be 
under Stack Overflow's CC BY-SA 3.0 instead of its original Apache
license. Second, if the code snippet is copied and incorporated into another
software project with a conflicting license, a legal issue may arise.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 801987 */             /* StringUtils.java (2013-02-05) */
public static String humanReadableInt(long number) {    public static String humanReadableInt(long number) {
  long absNumber = Math.abs(number);                      return TraditionalBinaryPrefix.long2String(number,"",1);
  double result = number;                               }
  String suffix = "";
  if (absNumber < 1024) {
  } else if (absNumber < 1024 * 1024) {
    result = number / 1024.0;
    suffix = "k";
  } else if (absNumber < 1024 * 1024 * 1024) {
    result = number / (1024.0 * 1024);
    suffix = "m";
  } else {
    result = number / (1024.0 * 1024 * 1024);
    suffix = "g";
  }
  return oneDecimal.format(result) + suffix;
}
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{StringUtils.java}}. The one from the
		Stack Overflow post 801987 (left) is outdated when compared to
		its latest version in the \textsf{Hadoop} code base
		(right). The toxic code snippet is outdated code, has race conditions, and does not contain its
		original Apache v.2.0 license.}
	\label{fig:before-after_2}
\end{figure*}

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{Hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{Hadoop}. We can see that
they are totally different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
\FIXME{I don't understand the following:} The absence of Apache v.2.0 license also occurs after the snippet is posted on 
Stack Overflow.

The two toxic code snippet in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times at
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet approximately every 5
days compared to almost every day for the second one. A quick web search shows
that the defective {\small{\texttt{humanReadableInt}}} method in the second
example already appears in approximately 500 projects on GitHub. Considering the
popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippets on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,302 online clones, at least 330 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 154 of them, we found evidence that they have been copied
	from a specific open source project. 101 of them we found to be outdated. %
	% and questionable for being reused.

	\item \textbf{Awareness of Stack Overflow answerers to toxic code snippets:} We
	performed an online survey and collected answers from 201 highly-ranked Stack
	Overflow users. We found that they cloned code snippets from open source
	projects to Stack Overflow answers. While Stack Overflow answerers are aware of
	their outdated code snippets, 19\% of the participants rarely
	or never fix the code. 99\% of the answerers never include a software
	license in their snippets and 69\% never check for licensing conflicts between the
	cloned code snippets and Stack Overflow's CC BY-SA 3.0.

@@

\textbf{Stack Overflow:} We extracted Java code snippets from a snapshot of a
Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. % The archived dump has a size of 9 gigabytes.
The data dump is in XML, and it contains information of posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode}
methods, which are not interesting for the study. Each snippet was extracted
from the dump and saved to a file. Moreover, we filtered out irrelevant code
snippets that were part of the accepted answers but were not written in Java by
using regular expressions and manual checking.
Finally we obtained 72,365 Java code snippets containing 1,840,581
lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
source code. The median size of the snippets is 17 lines.

@@

\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	%\small
	\begin{tabular}{lrrr}
		\toprule
		Data set & No. of files & SLOC & Median \\
		\midrule
		Stack Overflow & 72,365 & 1,840,581 & 17 \\ 
		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
		\bottomrule
	\end{tabular} 
\end{table}

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. %\textbf{Clone Detection and Configuration: }
There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to the nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution due to lexical errors. iClones
could complete its execution but skipped 367 snippets due to malformed blocks in
Stack Overflow data sets. CCFinder reported 8 errors while processing the two data sets. 
Although Simian, SourcererCC, and DECKARD
could successfully report clones, we decided to choose only Simian and
SourcererCC due to their fast detection speed. Moreover, Simian and
SourcererCC complement each other as SourcererCC's clone fragments are
always confined to method boundaries while Simian's fragments are not.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, emse, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2)~\cite{Bellon2007}. \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}.

@@

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016, emse}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. 
\FIXME{Something is not right: First it says that variable renaming is
  disabled, and later it is said that SourcererCC uses renaming.}
All variable renaming are disabled to decrease the number of
false positives since we aim for finding clones that are copied from open source
projects with minimal modifications. The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statements (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

We follow Bellon's original definitions of ok-match~\cite{Bellon2007}, which are based on how much two clone
fragments \textit{CF} are contained in each other:

%\squeezeup
%\begin{displaymath}
%overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
%\end{displaymath}
% \squeezeup
\begin{displaymath}
contained(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
\end{displaymath}
\noindent%
A clone pair \textit{CP} is formed by two clone fragments
\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} =
(\textit{CF$_1$}, \textit{CF$_2$})
%, and the \textit{good-value} and
and the \textit{ok-value} of two clone pairs is defined as

@@

Using the ok-match criterion with a predefined threshold \textit{t} of 0.7
similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC into a single set of 2,302 online
clone pairs. There are only 97 common clone pairs between the two clone sets 
as depicted in~\Cref{fig:clonemerging}.  The low number of common
clone pairs is due to SourcererCC reporting clones with method
boundaries while Simian is purely line-based.

@@

		UD & Cloned from each other or from an external source
                     \textit{X} outside the project (unknown)\\
		\midrule
		BP & Boiler-plate or IDE auto-generated \\

@@

\textbf{To answer RQ1, we found more than half (53\%) of Qualitas projects to share
	similar code with Stack Overflow code snippets. In the manually confirmed 
	data set of 2,302 clone pairs, we found 2,076 pairs as true positives which 
	account for 59 Qualitas projects and
	443 Stack Overflow code snippets.}
